Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-10-18 manuscript/bef_stability/manuscript.Rmd
Manuscript update: colin rreview + new table and figures

Both the relationship between diversity and ecosystem functioning, and that between food
web complexity and stability, have received considerable attention during the
last decades in ecology. The former relationship remains rarely investigated
in the context of food webs, especially in empirical studies explicitly
considering food web structures, the latter has been mainly the focus of
theoretical studies and empirical tests are critically missing. Here we link
species richness, food web structure and total biomass and its stability by
using a dataset of standardized fish sampling in French streams running from
1995 to 2018. We inferred trophic interactions thanks to recorded body size and
diet literature. We reveal that species richness and average trophic level had a
positive relationship with total biomass of fish communities while they had
respectively a negative and positive effect on its temporal stability. We
also found that the effects of stream size and temperature on total biomass and
stability are partly mediated by their effects on diversity and food web
structure. Overall, our study opens fruitful perspectives on the link between
species richness, network structure, ecosystem properties and their stability.

@@

Current biodiversity losses and global changes has the potential to affect
ecosystems in complex ways [@bellard_impacts_2012]. Biodiversity has a
tremendous effect on ecosystem properties because it largely determines both the
amount and the distribution of matter and energy fluxes
within and among ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
production [@tilman_productivity_1996; @cardinale_species_2002;
@grace_integrative_2016], distribution [@thebault_relationship_2006] and
stability [@thebault_trophic_2005; @thebault_relationship_2006;
@tilman_biodiversity_2006]. The relationship between biodiversity and
ecosystem properties is a central topic in ecology [@hector_plant_1999;
@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
@duffy_why_2009; @isbell_forest_quantifying_2018] and its documentation is thus
crucial to better anticipate the impacts of global change.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity and
total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
ecosystems and taxons studied, the relationship between diversity and ecosystem
functioning remains traditionally focused on single trophic levels, ignoring the
effects of food web structure. Theoretical models have recently extended
classical theoretical studies in plant communities [@tilman_plant_1997;
@loreau_biodiversity_2001] to food webs [@thebault_food-web_2003;
@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018].
These models show that both resource use complementarity and selection effects,
the two main mechanisms previously highlighted in single-trophic studies, are
also important to understand diversity effects in food webs
[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
However, they also reveal new mechanisms such as positive effects of diversity
of trophic levels, i.e. associated with higher trophic levels, on ecosystem
functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
web properties, such as interaction distribution and strength, affect the
distribution of biomass among adjacent trophic levels
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
We are lacking empirical studies that assess jointly how food web structure, in
conjunction with species diversity, affect total biomass production and other
ecosystem properties.

@@

Many studies showed that species richness increases temporal stability of
communities, i.e. variation through time, often quantified by the temporal CV.
Such positive relationships between species richness and temporal stability have
been reported in experimental grasslands and aquatic bacterial systems
[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
settings, such as stream fish communities [@franssen_annual_2011], bird and
butterfly communities [@olivier_urbanization_2020]. However, this relationship has
been mostly explored in single trophic level systems or without accounting for
food web structure, even more so than the relationship between diversity and biomass
production. Several theoretical studies at considering single trophic level have clarified which mechanisms
generate this positive relationship between species richness and temporal
stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
synchrony and (2) species variability. Species synchrony captures to what extent
the fluctuations of abundances or biomasses through time are correlated among
species. A low synchrony in species fluctuations, i.e. asynchrony, is
synonymous of compensatory dynamic, where the decrease in abundance of a species
is compensated by the increase of an other.  Asynchrony is generally the main
mechanism which species richness has a stabilizing effect on temporal
stability [@tilman_biodiversity_2006; @olivier_urbanization_2020].Though most often positive, the relationship between species diversity and asynchrony has also been evidenced to be neutral or negative in natural settings
[@tilman_biodiversity_2006; @thibaut_understanding_2013;
@olivier_urbanization_2020]. In addition to diversity, food web structure is
expected to strongly affect the stability of communities and ecosystems, as
outlined by the large body of theoretical studies on this topic [@may_will_1972;
@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
@stouffer_compartmentalization_2011]. In particular, predation has cascading
effects on both species variability and synchrony [@teng_dynamics_2004; @shanafelt_stability_2018] and it affects as
well synchrony between species. In spite a long-standing interest for the links between food web complexity and stability in ecology, to
date we have very few evidence on the relationship between network structure and
the temporal stability of species and total biomass in empirical multitrophic
communities.

@@

Overall, the evidence suggests that both species richness and network structure
should modulate total biomass and stability of communities. The effects of
species richness and network structure, such as connectance and average trophic
level, are potentially conflicting or synergistic in such a way that they need
to be addressed jointly. Yet, there is no direct empirical evidence to date for
the combined effects of species richness and network structure on total biomass
and stability in natural communities.

Although the relationships between diversity, total biomass and its stability in
natural systems can be similar to those found in experimental communities [e.g.,
@wu_relationship_2015; @li_relationship_2018], negative or non significant
effects of species richness on total biomass have for example been found in some
natural communities such as forests [@szwagrzyk_above-ground_2007;
@jacob_productivity_2010; @seidel_relationship_2013]. Some authors suggest that
the lack of resource complementarity or environmental harshness might be
responsible for negligible, or negative effects of species richness
[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015]. These
different relationships might also arise from effects of the environment on both
diversity and ecosystem functions [@loreau_biodiversity_2001].

@@

Environmental effects might also complicate (or obscure) the relationship
between diversity and structure in driving stability and biomass in natural
systems [@loreau_biodiversity_2001; @he_global_2013;
@grace_integrative_2016]. Environment affects organism performance directly, and
thereby, species abundances, total biomass [@grace_integrative_2016] and temporal
stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
For example, larger ecosystem might increase the number of available
resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
@li_relationship_2018 have notably shown that climate moisture has a positive
direct effect on total biomass, but also indirect through a positive effect on
species richness. Accounting for environment also allow for an overall
comparison of the strength of the effects of environment and community structure
on total biomass and its stability.

@@

Because their trophic interactions can be inferred, stream fish communities
constitute a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic
interactions are difficult to measure in natural conditions, a substantial body
of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Especially in stream communities, including fishes,
@brose_predator_2019 found that the prediction of predator prey trophic
interactions based on body size ratio was far better in stream ecosystems than
in other aquatic and terrestrial ecosystems. Lastly, most of the diversity-biomass and diversity-stability
relationships, have been assessed in terrestrial ecosystems while there is a
evident need to test such relationships in a variety of ecosystem types.

Our study aims to document the relationships between food web structure and
total biomass and its temporal stability in natural communities. To do so, we
used the ONEMA dataset consisting in standardized sampling of fish communities
in French streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10
years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
based on body size and diet. We question whether species richness,
connectance and average trophic level increase, decrease or are not related to
total biomass and its temporal stability. We further question whether the
species richness, connectance, and average trophic level have antagonistic or
synergistic effect on total biomass and its temporal stability. Finally, we
question if ecosystem size and average temperature increase total biomass and
its temporal stability.

@@

```{r}
matmet_cap <- paste0(
  #"(A) Conceptual model of the hypothesized relationships between environment,
  #species richness, network metrics and total biomass / biomass stability. ",
  #"Solid and dashed arrows represent respectively direct and indirect effects.
  #",
  #"The blue, green and blue/green dashed arrows being respectively indirect
  #effects going through species richness, network metrics and through both
  #species richness and network metrics.",
  "(A) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
  "Inner borders draw the limits of the hydrographic basins. ",
  "(B) The metaweb. Each trophic species (N = 412) is represented by a node and
  each color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
  "(C) Subset over network variation through time. The species names
  corresponding to the three digit codes are found in Table SXX."
)
```

```{r matmet, fig.cap = matmet_cap}
myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))

# Network inference
net_method_path <- mypath("manuscript/bef_stability/figs",
  "hypothesis.pdf")
metaweb_path <- mypath("manuscript/bef_stability/figs",
  "metaweb.png")
library(magick)

p_net_method <- cowplot::ggdraw() +
  cowplot::draw_image(magick::image_read_pdf(net_method_path))
p_metaweb <- cowplot::ggdraw() +
  cowplot::draw_image(magick::image_read(metaweb_path))

top <- plot_grid(p_net_method, p_st, ncol = 2, rel_widths = c(1, 1), labels =
  "AUTO")
bottom <- plot_grid(p_metaweb, temporal_network, ncol = 2,
  rel_widths = c(1, 1), labels = c("C", "D"))

left <- plot_grid(p_st, p_metaweb, ncol = 1, rel_widths = c(1, 1), labels =
  c("A", "B"))
p_test <- plot_grid(left, temporal_network, ncol = 2, labels = c("A", "C"))

p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
  labels = c("", "C"))
save_plot(
  filename = mypath("manuscript/bef_stability/figs",
    "method_fig.pdf"),
  p_test, nrow = 2, ncol =2,
  base_width = 7/2.54,
  base_asp = 0.3
)
p_test
```

@@

Fish communities were monitored across stream sections in France on the period
1995-2018 by the French Office of Water and Aquatic Ecosystems (ONEMA) using
electric fishing. Two different standardized protocols were used for small and
large streams (detailed in Supplementary material, part 1.1). For streams
shallower than 0.7m across the entire width, the sampling took place over the
whole width of the streams and was done by foot whereas in streams deeper than
0.7m, the sampling was done over the bank by foot or by boat. The sampling
season spanned from late spring to autumn. During sampling, all the fishes
caught were identified and recorded. For each species, either the body size of
all fish was measured, or a representative sample when the number of fish was
high (Figure S1, supplementary information). The fishes were released at the end
of the sampling. Additionally, the physical characteristics of the river was
recorded during sampling as well as the sampling effort, quantified as the
surface sampled (range XXX-XXX).

The stations where the stream was of intermediate size could be sampled
alternatively with one of the two sampling protocols. When it was the case, we
kept only the most frequently used sampling protocol. Finally, we kept stations
that had been sampled ten years or more. there was low heterogeneity of the sampling month
within stations, with the median sampled month being 
mid-August while the median of the standard deviation of the sampled month
within station was $0.7$. As the concept of community variability referred to variability
around an equilibrium, which is rarely observed or difficult to characterize in
natural communities, only those stations with no temporal trends in total
biomass were selected (detailed in supplementary methods). However, the results
were robust to the relaxation of this hypothesis (Supplementary results). These
selections resulted in 99 stations distributed over seven hydrographic basins
(Figure \@ref(fig:matmet) A).

@@

The body size of all fish individuals was not recorded when they were too
numerous. The body size of the unmeasured individuals was inferred under the
assumption that species body size followed a normal distribution whose mean and
standard deviation were quantified from the recorded individuals of the sampling
(See supplementary methods, Figure S1). The body mass of each individual was
then estimated using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$
being the body mass in grams, $l$ the body size in millimeters and $i$ the
individual), where the coefficients $0.01$ and $3.03$ comes from two
meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
biomass and total biomass at each sampling event was then calculated by summing
individual body masses. To account for the variation in sampling effort among
sites, species biomass and total biomass have been related to the surface
sampled, i.e.  $gm^{-2}$. In the analysis, the total biomass of a
station has been defined as the median of the total biomass acrossall times.

@@

In order to describe the mechanisms driving the temporal stability of biomass, we
decomposed the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
a
weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
@thibaut_understanding_2013:

@@

Species richness was computed as the total number of species present across all times
in a given station. As for biomass, we controlled species richness for sampling
effort by dividing the total number of species by the total surface sampled in
the given station. Species richness was then expressed in number of species by
square meter sampled.

### Network building

@@

Trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
throughout an individual's life, and thereby with body size. For example, alvins
feed on plankton while adults may feed on algae, fishes, with bigger individuals
eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body size classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, rather than species [@jennings_weak_2001].

The feeding interactions of a fish node, i.e a trophic species, were determined
by both its species identity and its body size. Then, species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature (cf Bonnaffe ref). Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

For a piscivorous trophic species, i.e. a piscivorous node, the fish-fish
trophic links was defined in two steps and based on the body size ratio between
predators and prey. First of all, the predation window of a piscivorous node was
defined as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
@claessen_impact_2002; @hart_handbook_2008]. Then, a trophic link was set
between the piscivorous node and every node whose midpoint
was included in the predation range (Figure S2). The fish-resource trophic
links were set between the trophic species and the resources nodes according the
food diet of their size class, for both the piscivorous and non piscivorous
trophic species. Lastly, the trophic links between resource nodes were set
according to the food diet data [@allan_stream_2007; @hart_handbook_2008].

@@

For each trophic network, corresponding to a particular site and year, we
computed two of the most commonly used network metrics to characterize food
webs, namely the connectance and mean trophic level. 
The networks metrics were also based on the trophic species,
i.e. body size classes. Connectance describes the level of generalism in the
network and is calculated as the actual number of
interactions divided by the maximum number of interactions if all species interact
together ($C = L / N^2$, L and N being resp. the number of links and of trophic
species plus resource nodes). The mean trophic level $\overline{T}$ was computed
as the mean trophic level weighted by the biomass of each trophic species
(excluding resource nodes for which we had no biomass information), so
$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and
$B_i$ being respectively the trophic level and the biomass of the node $i$. The
trophic level of the nodes was computed as one added to the average trophic
level of its food item. For each site, the median of connectance and average
trophic level over time was used in subsequent analysis.

# Select fishing operation 
myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

@@

mysave(habitat_press, habitat_pressure, dir = mypath("data"))

@@

```{r, message = FALSE, results = FALSE}
# Com
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
 type_network_metrics = "classes"
)
# Compute sem dataset
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )

@@

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for (A) biomass stability and
  (B) total biomass. ",
  "Results of the Structural Equation Models for (C) the
  determinants of biomass stability and (D) total biomass. Red and green
  represent respectively negative and positive path coefficients. The path
  coefficients are standardized coeffients. For convenience, only significant
  paths (i.e, *P < 0.05*) are shown."

@@

plot_grid(
  meta_stab_sem_rich, meta_bm_sem_rich,
  p_stab_sem_rich, p_bm_sem_rich,
  labels = LETTERS[1:4], nrow = 2,
  rel_widths = c(1, 1)
)
```

>>>>

Both the relationship between diversity and ecosystem functioning, and between food
web complexity and stability, have received considerable attention during the
last decades in ecology. The former relationship remains rarely investigated
in the context of food webs, especially in empirical studies explicitly
considering food web structures, the latter has been mainly the focus of
theoretical studies and empirical tests are critically missing. Here we link
species richness, food web structure and annual biomass and its temporal stability
using a dataset of standardized fish sampling in French streams running from
1995 to 2018. We inferred trophic interactions thanks to recorded body size and
diet literature. We reveal that species richness and average trophic level had a
positive relationship with annual biomass of fish communities while they had
respectively a negative and positive effect on its temporal stability. We
also found that the effects of stream size and temperature on annual biomass and
stability are partly mediated by their effects on diversity and food web
structure. Overall, our study opens fruitful perspectives on the link between
species richness, network structure, ecosystem properties and their stability.

@@

Current biodiversity losses and further global change has the potential to affect
ecosystems in complex ways [@loreau_biodiversity_2001; @tilman_biodiversity_2014]. Biodiversity has a
tremendous effect on ecosystem properties because it largely determines both the
amount and the distribution of matter and energy fluxes
within and among ecosystems [@loreau_meta-ecosystems:_2003]. Biodiversity thus affects biomass
production [@tilman_productivity_1996; @cardinale_species_2002;
@grace_integrative_2016], distribution [@thebault_relationship_2006] and
stability [@thebault_trophic_2005; @thebault_relationship_2006;
@tilman_biodiversity_2006]. The relationship between biodiversity and
ecosystem properties is a central topic in ecology [@hector_plant_1999;
@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
@duffy_why_2009; @isbell_forest_quantifying_2018] and our understanding of it is 
crucial to better anticipate the impacts of global change.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity and
total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
ecosystems and taxons studied, the relationship between diversity and ecosystem
functioning remains traditionally focused on single trophic levels, ignoring the
effects of food web structure. Theoretical models have recently moved from
single trophic [@tilman_plant_1997;
@loreau_biodiversity_2001] to multitrophic communities [@thebault_food-web_2003;
@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018]. 
These models show that both resource use complementarity and selection effects,
the two main mechanisms previously highlighted in single-trophic studies, are
also important to understand diversity effects in food webs
[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
However, they also reveal new mechanisms such as positive effects of 
the number of trophic levels, i.e. associated with higher trophic levels, on ecosystem
functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
web properties, such as interaction distribution and strength, affect the
distribution of biomass among adjacent trophic levels
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
Despite these theoretical evidences that structure affects biomass, we are
lacking empirical studies that assess jointly how food web structure and species
diversity affect total biomass and its production.

@@

Further than biomass production, many studies showed that species richness
increases temporal stability of communities, i.e. variation through time, often
quantified by the temporal CV of biomass.  Such positive relationship between
species richness and temporal stability of biomass has been reported in
experimental grasslands and aquatic bacterial systems
[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
settings, such as stream fish communities [@franssen_annual_2011], bird and
butterfly communities [@olivier_urbanization_2020]. However, this relationship
has been mostly explored in single trophic level systems or without accounting
for food web structure, even more so than the relationship between diversity and
biomass production.

Several theoretical studies considering single trophic level have
clarified which mechanisms generate this positive relationship between species
richness and temporal
stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
synchrony and (2) species variability. Species synchrony captures to what extent
the fluctuations of abundances or biomasses through time are correlated among
species. A low synchrony in species fluctuations, i.e. asynchrony, is
synonymous of compensatory dynamic, where the decrease in abundance of a species
is compensated by the increase of an other. Asynchrony is generally the main
mechanism which species richness has a stabilizing effect on temporal
stability [@tilman_biodiversity_2006; @olivier_urbanization_2020]. Asynchrony is
expected to raise with the variability of species responses to perturbations. Though most
often positive, the relationship between species diversity and asynchrony has
also been evidenced to be neutral or negative in natural settings
[@tilman_biodiversity_2006; @thibaut_understanding_2013;
@olivier_urbanization_2020; @valencia_synchrony_2020].

In addition to diversity,
food web structure is expected to strongly affect the stability of communities
and ecosystems, as outlined by the large body of theoretical studies on this
topic [@may_will_1972; @dunne_network_2006; @neutel_reconciling_2007;
@duffy_why_2009; @stouffer_compartmentalization_2011]. In particular, predation
has cascading effects on both species variability and synchrony
[@teng_dynamics_2004; @shanafelt_stability_2018] and it also affects
synchrony between species.

@@

Overall, the evidence suggests that both species richness and network structure
should modulate total biomass and stability of communities. The effects of
species richness and network structure, such as connectance and average trophic
level, are potentially conflicting or synergistic in such a way that they need
to be addressed jointly. Despite the long-standing interest for the links
between food web complexity and stability in ecology, we still have very few
evidence of the relationship between network structure and the temporal
stability of multitrophic communities in natural settings.
Although the relationships between diversity, total biomass and its stability
found in experimental and in natural settings can be similar
[e.g., @wu_relationship_2015; @li_relationship_2018], negative or non
significant effects of species richness on total biomass have been found in some
natural communities such as forests [@szwagrzyk_above-ground_2007;
@jacob_productivity_2010; @seidel_relationship_2013]. Some authors suggest that
the lack of resource complementarity or environmental harshness might be
responsible for negligible, or negative effects of species richness
[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015].

@@

When analyzing data from natural communities, the relationships among species
richness, total biomass and species richness might also arise from effects of
the environment on both diversity and ecosystem functions
[@loreau_biodiversity_2001; @he_global_2013;
@grace_integrative_2016]. Environment affects organism performance directly, and
thereby, species abundances, total biomass [@grace_integrative_2016] and temporal
stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
For example, larger ecosystem might increase the number of available
resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
@li_relationship_2018 have notably shown that climate moisture has a positive
direct effect on total biomass, but also indirect through a positive effect on
species richness. Accounting for environment also allow for an overall
comparison of the strength of the effects of environment and community structure
on total biomass and its stability.

@@

Because their trophic interactions are well known, stream fish communities
constitute a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic
interactions are difficult to measure in natural conditions, a substantial body
of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Especially in stream communities, including fishes,
@brose_predator_2019 found that the prediction of predator prey trophic
interactions based on body size ratio was far better in stream ecosystems than
in other aquatic and terrestrial ecosystems. Lastly, most of the
diversity-biomass and diversity-stability relationships, have been assessed in
terrestrial ecosystems while there is a evident need to test such relationships
in a variety of ecosystem types.

Our aim is to document the relationships among species richness, food web structure, 
total biomass and its temporal stability in natural communities. To do so, we
used the ONEMA dataset consisting in standardized sampling of fish communities
in French streams [@edeline_ecological_2013]. We selected 99 sites that were sampled for more than 10
years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
based on body size and diet. We question whether species richness, connectance
and average trophic level increase, decrease or are not related to
total biomass and its temporal stability. We further question whether the
species richness, connectance, and average trophic level have antagonistic or
mutual effect on total biomass and its temporal stability. Finally, we
question if ecosystem size and average temperature increase total biomass and
its temporal stability.

@@

```{r}
matmet_cap <- paste0(
  #"(A) Conceptual model of the hypothesized relationships between environment,
  #species richness, network metrics and total biomass / biomass stability. ",
  #"Solid and dashed arrows represent respectively direct and indirect effects.
  #",
  #"The blue, green and blue/green dashed arrows being respectively indirect
  #effects going through species richness, network metrics and through both
  #species richness and network metrics.",
  "Yearly temporal series of networks of two stations having respectively a low (A) and high
  (B) temporal stability of biomass. A and B stations have respectively the
  closest stability to the first and third quartile of the distribution of the
  temporal stability of biomass in the dataset. Point size are proportional to
  the biomass of the trophic species.  (C) Observation sites (black dots) were
  located across France and monitored on the period 1995-2018. ", "Grey shades
  highlighted elevalation variation. ", "Inner borders draw the limits of the
  hydrographic basins. ", "(D) The metaweb. Each trophic species (N = 412) is
  represented by a node and each color represent a species (S = 45). Resource
  nodes (7) were drawn in grey. ", "The species names corresponding to the three
  digit codes are found in Table SXX."
)
```

```{r matmet, fig.cap = matmet_cap, results = "fig.show"}
library(knitr)
include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
```

# Select fishing operation 
myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
range_surface <- map_dbl(c(min, max), ~.x(op_analysis_bbb$surface, na.rm =TRUE))
# quantile(op_analysis_bbb$surface, na.rm =TRUE)
```

@@

Fish communities were monitored across stream sections in France on the period
1995-2018 by the French Office of Water and Aquatic Ecosystems (ONEMA) using
electric fishing. Two different standardized protocols were used for small and
large streams (detailed in Supplementary material, part 1.1). For streams
shallower than 0.7m across the entire width, the sampling took place over the
whole width of the streams and was done by foot whereas in streams deeper than
0.7m, the sampling was done over the bank by foot or by boat. The sampling
season spanned from late spring to autumn. One sampling event correspond to a
sampling a given year in a given sampling station. During sampling, all the
fishes caught were identified. For each species, either the body size of all
fish was measured, or a representative sample when the number of fish was high
(Figure S1, supplementary information). The fishes were released at the end of
the sampling. Additionally, the physical characteristics of the stream were 
recorded during sampling event as well as the sampling effort, quantified as the
surface sampled (range `r range_surface[1]`-`r range_surface[2]` square metres).

The stations where the stream was of intermediate size could be sampled
alternatively with one of the two sampling protocols. In this case, we
kept only the most frequently used sampling protocol. Then, we selected the
stations that had been sampled ten years or more. There was low heterogeneity of
the sampling month within stations, with the median sampled month being
mid-August while the median of the standard deviation of the sampled month
within station was $0.7$. As the concept of community variability referred to
variability around an equilibrium, which is rarely observed or difficult to
characterize in natural communities, only stations with no temporal trends
in total biomass were selected (detailed in supplementary methods). However, the
results were robust to the relaxation of this hypothesis (Supplementary
results). These selection steps resulted in 99 stations distributed over seven
hydrographic basins (Figure \@ref(fig:matmet) A).

@@

The body size of all fish individuals was not recorded when they were too
numerous. The body size of the unmeasured individuals was inferred under the
assumption that species body size followed a normal distribution whose mean and
standard deviation were quantified from the recorded individuals of the sampling
(See supplementary methods, Figure S1). The body mass of each individual was
then estimated using an allometric law $B_i = 0.01 \times l_i^{3.03}$, $B$
with the body mass in grams, $l$ the body size in millimeters, $i$ the
individual and where the coefficients $0.01$ and $3.03$ comes from two
meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
biomass and total biomass at each sampling event was then calculated by summing
individual body masses. To account for the variation in sampling effort among
sites, species biomass and total biomass have been related to the surface
sampled, i.e. $gm^{-2}$. In the analysis, the total biomass of a
station has been defined as the median of the total biomass across sampling
events.

@@

We described the mechanisms driving the temporal stability of biomass, by
decomposing the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
a weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
@thibaut_understanding_2013:

@@

Species richness was computed as the total number of species present across
sampling events 
in a given station. As for biomass, we controlled species richness for sampling
effort by dividing the total number of species by the total surface sampled in
the given station. Species richness was then expressed in number of species per 
square meter sampled.

### Network inference

@@

Trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as for many organisms, shifts
throughout an individual's life, and thereby with body size. For example, alvins
feed on plankton while adults may feed on algae and fishes, with bigger individuals
eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body size classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, than species [@jennings_weak_2001].

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. Species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature (cf Bonnaffe ref). Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

For a piscivorous trophic species, the fish-fish
trophic links was defined in two steps and based on the body size ratio between
predators and prey. First of all, the predation window of a piscivorous trophic specie was
defined as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
@claessen_impact_2002; @hart_handbook_2008]. Then, a trophic link was set
between the piscivorous trophic species and every trophic species whose midpoint
was included in the predation window (Figure S2). The fish-resource trophic
links were set between the trophic species and the resources nodes according the
food diet of their size class, for both the piscivorous and non piscivorous
trophic species. Lastly, the trophic links among resource nodes were set
according to the literature [@allan_stream_2007; @hart_handbook_2008].

@@

For each trophic network, corresponding to a particular site and year, we
computed two of the most commonly used network metrics to characterize food
webs, namely the connectance and mean trophic level. Connectance describes the
level of generalism in the network and is calculated as the actual number of
interactions divided by the maximum number of interactions if all species interact
together ($C = L / N^2$, L and N being resp. the number of links and of trophic
species plus resource nodes). The mean trophic level $\overline{T}$ was computed
as the mean trophic level weighted by the biomass of each trophic species
(excluding resource nodes for which we had no biomass information), so
$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and
$B_i$ being respectively the trophic level and the biomass of the node $i$. The
trophic level of the nodes was computed as one added to the average trophic
level of its food item. For each site, the median of connectance and average
trophic level over time was used in subsequent analysis.

@@

mysave(habitat_press, habitat_pressure, dir = mypath("data"), overwrite = TRUE)

@@

```{r, message = FALSE, results = FALSE}
# Com
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
 type_network_metrics = "classes"
)
# Compute sem dataset
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )
mysave(sem_data, dir = mypath("data"), overwrite = TRUE)
```

@@

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for (A) biomass stability and
  (B) total biomass. ",
  "Results of the Structural Equation Models for (C) the
  determinants of biomass stability and (D) total biomass. Red and green
  represent respectively negative and positive path coefficients. The path
  coefficients are standardized coeffients. For convenience, only significant
  paths (i.e, *P < 0.05*) are shown. Rsq: Ajusted R square."

@@

plot_grid(
  meta_bm_sem_rich, p_bm_sem_rich,
  meta_stab_sem_rich, p_stab_sem_rich,
  labels = LETTERS[1:4], nrow = 2,
  rel_widths = c(1, 1)
)
```
